A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-04-27 paper.tex
Leonid's affiliation
Fixes to the example introduction

@@

@@

\institute{NICTA\thanks{NICTA is funded by the Australian Government as represented by the Department of Broadband,
    Communications and the Digital Economy and the Australian Research Council through the ICT
    Centre of Excellence program.} and UNSW \\
    \email{alexander.legg@nicta.com.au}
    \and Samsung Research America}

@@

First, we introduce a running example to assist the explanation. We consider a
simple arbiter system in which the environment requests for either 1 or 2
resources, and the controller may grant access to two resources. The controller
must ensure that the number of unhandled requests is not $\geq 3$.
Figure~\ref{fig:example} shows the variables (\ref{fig:examplevars}) and the
formulas for computing next-state variables (\ref{fig:exampletrans}) for this
example.

\begin{figure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \begin{tabular}{l | l | l}
            \textbf{Controllable} & \textbf{Uncontrollable} & \textbf{State} \\
            \hline
            \texttt{request = \{1, 2\}} & \texttt{grant0 = \{0, 1\}} & \texttt{resource0 = \{0, 1\}} \\
            & \texttt{grant1 = \{0, 1\}} & \texttt{resource1 = \{0, 1\}} \\
            & & \texttt{nrequests = \{0, 1, 2, 3\}} \\
        \end{tabular}
        \caption{Variables}
        \label{fig:examplevars}
    \end{subfigure}

@@

If the dual solver can find no spoiling strategy at any of the leaves, then the
candidate partial strategy is a winning one. Otherwise, \textsc{verify} returns
the move used by the opponent to defeat a leaf of the partial strategy, which
is appended to the corresponding node in $T$ in order to refine it in line~(9).
In our example, the controller's partial strategy in Figure~\ref{fig:strategy}
is defeated by the counterexample action \texttt{req=2}.
Figure~\ref{fig:refined} shows a refined AGT that includes this action.

>>>>

\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}

@@

\newtheorem*{exmp}{Example}

@@

\institute{NICTA\thanks{NICTA is funded by the Australian Government as represented by the Department of Broadband,
    Communications and the Digital Economy and the Australian Research Council through the ICT
    Centre of Excellence program.} and UNSW \\
    \email{alexander.legg@nicta.com.au}
    \and Samsung Research America\thanks{Work completed at 
    Carnegie Mellon University}}

@@

\begin{exmp}
We introduce a running example to assist the explanation. We consider a
simple arbiter system in which the environment requests for either 1 or 2
resources, and the controller may grant access to two resources. The total
number of requests grows each round by the number of environment requests and
shrinks by the number of resources granted by the controller in the previous
round.  The controller must ensure that the number of unhandled requests does
not accumulate to more than 2.  Figure~\ref{fig:example} shows the variables
(\ref{fig:examplevars}) and the formulas for computing next-state variables
(\ref{fig:exampletrans}) for this example. We use primed identifiers to denote
next-state variables and curly braces to define the domain of a variable.

This example is the $n=2$ instance of the more general problem of an arbiter of
$n$ resources. The set of winning states grows exponentially with the number of
resources the controller could use to grant requests, which makes the problem
hard for BDD solvers. This example illustrates the strength of the approach
presented here, which does not need to enumerate all winning states as will be
shown in Section~3.

\end{exmp}

\begin{figure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \begin{tabular}{l | l | l}
            \textbf{Controllable} & \textbf{Uncontrollable} & \textbf{State} \\
            \hline
            \texttt{request : \{1, 2\}} & \texttt{grant0 = \{0, 1\}} & \texttt{resource0 = \{0, 1\}} \\
            & \texttt{grant1 : \{0, 1\}} & \texttt{resource1 = \{0, 1\}} \\
            & & \texttt{nrequests : \{0, 1, 2, 3\}} \\
        \end{tabular}
        \caption{Variables}
        \label{fig:examplevars}
    \end{subfigure}

    \begin{subfigure}[t]{\textwidth}
        \centering
        \texttt{resource0 = 0; resource1 = 0; nrequests = 0;}
        \caption{Initial State}
        \label{fig:exampleinit}
    \end{subfigure}

@@

If the dual solver can find no spoiling strategy at any of the leaves, then the
candidate partial strategy is a winning one. Otherwise, \textsc{verify} returns
the move used by the opponent to defeat a leaf of the partial strategy, which
is appended to the corresponding node in $T$ in order to refine it in line~(9).

\begin{exmp}
    The controller's partial strategy in
    Figure~\ref{fig:strategy} is defeated by the counterexample action
    \texttt{req=2}.  Figure~\ref{fig:refined} shows a refined AGT that includes
    this action.
\end{exmp}
